Combining parsing with sentence understanding

### 2016-03-10 writing/hard_stack_paper/paper.tex
Initial abstract.

\title{Tree-structured neural networks revisited}

@@

\begin{document}
\maketitle
\begin{abstract}
\begin{itemize}
\item TreeRNNs are great, don't work for big data.
\item We present the transition-based TreeRNN implementation -- makes efficient training possible, show that it helps relative to seq models.
\item Further, attention has proven powerful for extending sequence models. We introduce constituent-by-constituent attention, and find it to be effective here, too.
\end{itemize}
\end{abstract}

\todo{Anonymize.}
\todo{Name the damn model!}

@@

\paragraph{Representing the stack in memory} Or, thin stack. 
\todo{[JG] Explain.}

@@

We evaluate five models on the SNLI task. Each uses 150d hidden states: 
\begin{itemize}
\item A baseline LSTM model (similar to that of \citealt{snli:emnlp2015}) that uses the same classifier architecture as our models, but encodes sentences using a single layer LSTM RNN sequence model.
\item The unaugmented transition-based sentence model.
\item The transition-based sentence model with the tracking LSTM.
\item The transition-based sentence model with the tracking LSTM and sequence-based attention over premise states.
\item The transition-based sentence model with the tracking LSTM and tree-based attention over premise states.
\end{itemize}

@@

                        & 1.4m               &   92.3   &   89.1      \\
\midrule
\multicolumn{4}{c}{New results}\\
\midrule
\result{150d LSTM RNN      }     & ?                  &   ?      &   81?       \\
\result{150d TB TreeLSTM}   
                        & ?                  &   ?      &   81?       \\
\result{150d TB TreeLSTM w/ tracking    }
                        & ?                  &   ?      &   83?       \\
\result{150d TB TreeLSTM w/ tracking, sequence-based attn.   }     
                        & ?                  &   ?      &   85+?       \\
\result{150d TB TreeLSTM w/ tracking, tree-based attn. }           
                        & ?                  &   ?      &   \textbf{?}\\
    \bottomrule
  \end{tabular}
  \protect\caption{\protect\label{tab:results}Results on SNLI 3-way inference classification. All reported figures are percent accuracy. \result{[JG]Add seconds-per-step *if* we get a reasonably well-optimized model in time.}} 
\end{table*}

>>>>

\title{Combining parsing with sentence understanding}

@@

\begin{document}
\maketitle
\begin{abstract}

Tree-structured neural networks are linguistically principled models for sentence encoding that have proven effective on several natural language understanding tasks. However, these models can only operate on parsed sentences, and do not support batched computation, making them prohibitively slow for large-scale tasks. We present the parser--interpreter neural network, or PINN, which implements the sentence encoding computations of a tree-structured neural network within the structure of a transition-based neural constituency parser. This model addresses both of the weaknesses of existing tree-structured models: the transition-based architecture of the parser makes it possible to perform tree-structured sentence interpretation in an efficient, batched, setting, and the deep integration with the parser allows the model to handle interpret unparsed data at test time with nearly no loss in accuracy. Finally, we show that this architecture supports a novel and effective method for handling local context in sentence interpretation, and integrates will with soft attention methods for sentence pair tasks.

\end{abstract}

\todo{Anonymize.}
\todo{Fill in name where needed.}
\todo{SST!}
\todo{Model 1!}

@@

\paragraph{Representing the stack in memory} Or, thin stack. And the cursor strategy for the buffer. 
\todo{[JG] Explain.}

@@

We evaluate five models on the SNLI task. Each uses 300d hidden states: 
\begin{itemize}
\item A baseline LSTM model (similar to that of \citealt{snli:emnlp2015}) that uses the same classifier architecture as our models, but encodes sentences using a single layer LSTM RNN sequence model.
\item The unaugmented transition-based sentence model.
\item The transition-based sentence model with the tracking LSTM.
\item The transition-based sentence model with the tracking LSTM and sequence-based attention over premise states.
\item The transition-based sentence model with the tracking LSTM and tree-based attention over premise states.
\end{itemize}

@@

                        & 1.4m               &   92.3   &   89.1      \\
\midrule
\multicolumn{4}{c}{New results}\\
\midrule
\result{300d LSTM RNN      }     & ?                  &   ?      &   81?       \\
\result{300d TB TreeLSTM}   
                        & ?                  &   ?      &   81?       \\
\result{300d TB TreeLSTM w/ tracking    }
                        & ?                  &   ?      &   83?       \\
\result{300d TB TreeLSTM w/ tracking, sequence-based attn.   }     
                        & ?                  &   ?      &   85+?       \\
\result{300d TB TreeLSTM w/ tracking, tree-based attn. }           
                        & ?                  &   ?      &   \textbf{?}\\
    \bottomrule
  \end{tabular}
  \protect\caption{\protect\label{tab:results}Results on SNLI 3-way inference classification. All reported figures are percent accuracy. \result{[JG]Add seconds-per-step *if* we get a reasonably well-optimized model in time.}} 
\end{table*}
